### 2016-11-16 src/local.tex
fig-conflict

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time.

>>>>

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time - $O(n^{Ck + 1})$.

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm,
we build the \emph{conflict graph} of the two solutions in which each node
represents a star from the optimal solution and edges exits between two nodes if
the local search solution has at least one edge that connects two stars, formally 
$G_\text{conflict} = (V, E)$ 
where $\{v_i : s_i \in M^* \}$ 
and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.

\begin{figure}[h]
\centering
\input{fig-conflict}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{subfloat:input} 
a directed graph with capacities on the vertices and weights on the edges. 
\subref{subfloat:output}
a feasible matching with total weight of 26.
$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
}
\end{figure}
